Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-25 lloveras_2020.tex
cambios de nishtha

We perform MHD modeling of the two target rotations studied with DEMT. For this propose we use the MHD coronal model AWSOM which addresses coronal heating by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
The model accounts for anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature. The dissipated turbulent energy is distributed over these three temperatures based on the theories of linear wave damping and stochastic heating. AWSoM does not use ad-hoc heating functions and accounts for both collisional and collision-less electron heat conduction. The Alfv\'{e}n wave number associated with the damping rate is determined by the critical balance condition which uses the cascade time of the minor wave \citep{Lit2007} instead of the previously used cascade time of the major wave \citep{Cha2011, Van2014}. This energy partitioning, in the improved version of AWSoM, leads to more electron heating and less solar wind acceleration.% \diego{falta cita}%\citep{Van2019b}.
To solve anisotropic MHD equations with radiative cooling, heat conduction and wave turbulence, AWSoM uses the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme. MHD equations employed within the AWSoM model are detailed in \citet{Van2014}. Recently, \citet{sachdeva_2019} validated the AWSoM simulation results with a suite of observations from near the Sun upto 1 AU for solar minimum conditions.

Global maps of the observed photospheric magnetic field are essential for accurate modeling of the solar corona and are the primary input for AWSoM. The model use GONG synoptic map as input for CR-2082 and ADAPT-GONG global magnetic field map for CR-2208. ADAPT-GONG maps are unavailable for CR-2082. GONG provides synoptic full disk line-of-sight surface map of the radial magnetic field component. The unobserved polar fields in GONG are estimated by fitting a polynomial to neighboring observed fields. An improvement over these maps is provided by the ADAPT model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation to evolve the magnetic field. These maps provide a physics based description of the unobserved polar fields \citep{Arg2010, Hen2012}. 
In AWSoM, the 2D radial photospheric field is used as a boundary condition for the 3D PFSS model which, in turn is used to specify the initial condition. We take the source surface to be at $2.5 \, \mrsun$ and the magnetic field is radial at this height. The radial component specifies the boundary condition.
%ADAPT-GONG maps have multiple realizations based on how the polar fields are filled. We use realization 5 for CR2208.
Based on \citet{Cha2011} the stochastic heating exponent is taken to be 0.21 and amplitude is 0.18 to account for energy partioning between electrons and protons. The Alfv\'{e}n wave energy boundary condition is given by the poynting flux (S$_{A}$) of the outgoing wave $(\frac{S_{A}}{B})_{\odot} = 1.0\times 10^{6}$ Wm$^{-2}$T$^{-1}$ and the correlation length of the Alfv\'{e}n waves is set to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$ m$\sqrt{T}$.

The base of the transition region (TR) forms the inner boundary of the model (at $\approx$1.0\,\rsun). To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot}=2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K. The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}. In reality, the thin transition has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses. To resolve these gradients excessive numerical resources are required. As described in \citet{Lio2009} and \citet{Sok2013}, we artificially broaden the transition region to resolve with our finest grid resolution of $\le$ 0.001\,\rsun. This broadening pushes the corona outwards. At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region. Consequently, AWSoM results below {$\approx 1.05\,\mrsun$} were not taken into account in this article.
\\
The computational domain for solar corona extends from 1 to 24 R$_{\odot}$. The spherical grid is radially stretched (with a maximum resolution of $0.001 \, \mrsun$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh Refinement resolves the angular size to 1.4$^\circ$ between $1 - 1.7 \, \mrsun$ and $2.8 \, \mrsun$ outside. The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid block. Local time stepping is used to speed up the steady state convergence. AWSoM simulation results provide the 3D distribution of density and temperature in addition to the 3D magnetic structure and velocity of the solar wind.

@@

{Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry. Rotation CR-2082} showed two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}. {Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}

@@

{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively higher densities and temperatures in comparison to the CHs. They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 24 and 25}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the declining phase of {SC 25, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious. This thermodynamic structure} of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.

@@

{Type 0 (small down) legs mainly populate the equatorial latitudes. This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level {around the solar minimum between SCs 24 and 25} by \citet{nuevo_2013}. Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}. Here, we verify the existence of this type of structure for the two target rotations. The relatively smaller population of down legs seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}. Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt. Finally, type III (open) legs populate the CHs.}

>>>>

We compare the DEMT analysis of the two Carrington rotations with the MHD model simulations results from the Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the SWMF. 
AWSoM is a three-temperature, MHD model of the solar corona and inner heliosphere which provides the 3D distribution of density and temperatures as well as the 3D magnetic structure and velocity of the solar wind. In this work, we use AWSoM model simulated results below 1.25 $\mrsun$ to correspond to the DEMT analysis region.
AWsoM addresses the heating of the solar corona by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade. This dissipated turbulent energy is distributed over anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature using theories of linear wave damping and stochastic heating.
AWSoM accounts for both collisional and collision-less electron heat conduction and does not use ad-hoc heating functions. The extended MHD equations including radiative cooling, heat conduction and wave turbulence within AWSoM \citep{Van2014} are solved using the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme. In the previous version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}. However, we improve the energy partitioning by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}. This leads to more electron heating and less solar wind acceleration \citep{Van2019b}.

The inner boundary of AWSoM is located at the base of the transition region (at $\approx$1.0\,$\mrsun$). In reality, the thin transition region has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses. To resolve these gradients in a global model would require excessive numerical resources. As described in \citet{Lio2009} and \citet{Sok2013} we artificially broaden the transition region to resolve with our finest grid resolution of 0.001\,$\mrsun$.  To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K. The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}.  At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region. Since the broadening of the transition region pushes the corona outwards, AWSoM results below 1.05 $\mrsun$ were not taken into account in this article.

To drive our solar corona model, accurate estimates of the photospheric magnetic field of the Sun form the primary input. Synoptic magnetograms are used to specify the initial and the boundary conditions of the magnetic field in AWSoM. We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics. The source surface is taken to be at 2.5 $\mrsun$. The Global Oscillation Network Group (GONG) provides synoptic full-disk surface maps of the radial magnetic field component of the Sun. However, since the polar regions are not well observed from the ecliptic, GONG estimates the polar fields by fitting a polynomial to neighboring observed latitudes, which might lead to inaccuracies. An improvement over these maps is provided by the Air Force Data Assimilation Photospheric Flux Transport (ADAPT) model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation. These maps provide a physics-based description of the unobserved polar magnetic fields \citep{Arg2010, Hen2012}. In this work, we use the GONG synoptic map as input for CR-2082 (ADAPT-GONG maps are unavailable for CR-2082) and the ADAPT-GONG global magnetic field map for CR-2208.  For CR-2082, the magnetic field from the GONG map is scaled up by a factor of 1.85 (for Br$<$5 G) while no modification is done for the ADAPT-GONG map for CR-2208. The AWSoM steady-state simulation set-up and input parameters for both rotations are described below.

To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent to be 0.21 and the amplitude equal to 0.18 for both rotations. The boundary condition for Alfv\'{e}n wave energy is given by the poynting flux (S$_{A}$) of the outgoing wave. $(\frac{S_{A}}{B})_{\odot} = 1.1\times 10^{6}$ Wm$^{-2}$T$^{-1}$ and  $1.0\times 10^{6}$ Wm$^{-2}$T$^{-1}$ for CR-2082 and CR-2208 respectively. $B_{\odot}$ is the filed strength at the inner boundary. The correlation length of the Alfv\'{e}n waves is set to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$ m$\sqrt{T}$.
%ADAPT-GONG maps have multiple realizations based on how the polar fields are filled. We use realization 5 for CR-2208.
The computational domain for solar corona extends from 1 to 24 R$_{\odot}$. The spherical grid in the solar corona is radially stretched (with a maximum resolution of 0.001 R$_{\odot}$ near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh Refinement (AMR) resolves the angular cell size to 1.4$^\circ$ between 1 - 1.7 $\mrsun$ and 2.8 $\mrsun$ outside. The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082. Local time stepping is used to speed up the steady state convergence. The AWSoM simulation results of the structure of the solar corona for solar minimum conditions represented by CR-2082 and CR-2208 are compared to the DEMT as described in the results section.

@@

{Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry. Rotation CR-2082} showed two {small} ARs, both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg$  \diego{(too smal to be registered)}. {Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$ \diego{(NOAA 12722, 12721)}.}

@@

{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively higher densities and temperatures in comparison to the CHs. They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between \diego{SCs 23 and 24}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the declining phase of \diego{SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious. This thermodynamic structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.

@@

{Type 0 (small down) legs mainly populate the equatorial latitudes. This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between \diego{SCs 23 and 24} by \citet{nuevo_2013}. Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}. Here, we verify the existence of this type of structure for the two target rotations. The relatively smaller population of down legs seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}. Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt. Finally, type III (open) legs populate the CHs.}
